---
title: "Summary of models trained"
author: "Team 1"
date: "09/10/2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE)
```

# Summary of trained model performance
First we load the models.
```{r}

library(plyr)
library(caret)
library(e1071)
rm(list=ls())
load(file = "DataWrangling/Featuresselected.RData")
load(file = "Models/SVMradmodel.RData")
load(file = "Models/svmpolymodel.RData")
load(file = "Models/svmlinmodel.RData")
load(file = "Models/RF.RData")
load(file = "Models/Neural_Network.RData")
load(file = "Models/NB.RData")
load(file = "Models/LR.RData")
load(file = "Models/LDAmodel.RData")
load(file = "Models/knnmodel.RData")
train.df$Cath <- as.factor(ifelse(train.df$Cath == 0,"N","Y"))
test.df$Cath <- as.factor(ifelse(test.df$Cath == 0,"N","Y"))
```

## Individual Models

Here is a summary of the performance of our individual models.

### k-Nearest Neighbours
```{r}
knn_result <- predict(knn.model, test.df[knn.features])
confusionMatrix(knn_result,test.df$Cath)
```
### Linear Discriminant Analysis
```{r}
lda_result <- predict(lda.model, test.df[lda.features$optVariables])
confusionMatrix(lda_result,test.df$Cath)
```

### Logistic Regression
```{r}
lr_result <- as.factor(ifelse(predict(LR_model, test.df[lr.features$optVariables])==1,"Y","N"))
confusionMatrix(lr_result,test.df$Cath)
```

### Naive Bayes
```{r}
nb_result <- as.factor(ifelse(predict(NB_model, test.df[nb.features$optVariables])==1,"Y","N"))
confusionMatrix(nb_result,test.df$Cath)
```

### Random Forest
```{r}
rf_result <- as.factor(ifelse(predict(RF_model, test.df[rf.features$optVariables])==1,"Y","N"))
confusionMatrix(rf_result,test.df$Cath)
```

### Neural Network
```{r}
nn_result <- as.factor(ifelse(predict(nn1, test.df)==1,"Y","N"))
confusionMatrix(nn_result,test.df$Cath)
```

### Support Vector Machines: Linear kernal
```{r}
svm_lin_result <- predict(svmlin.model, test.df[svmlin.features$optVariables])
confusionMatrix(svm_lin_result,test.df$Cath)
```

### Support Vector Machines: Polynominal kernal
```{r}
svm_poly_result <- predict(svmpoly.model, test.df[svmpoly.features$optVariables])
confusionMatrix(svm_poly_result,test.df$Cath)
```

### Support Vector Machines: Radial Basis kernal
```{r}
svm_rad_result <- predict(svmrad.model, test.df[svmrad.features$optVariables])
confusionMatrix(svm_rad_result,test.df$Cath)
```

## Ensemble Models


